Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older

### 2024-01-03 Manuscript Analyses/manuscript_analysis.Rmd
overall participant demographics

TBD

@@

>>>>

The overall demographic information for the participants are below.

@@

demo_table <- demo %>%
  dplyr::select(-id) %>%
  tbl_summary(type = list(age ~ "continuous",
                          gender ~ "categorical",
                          race ~ "categorical",
                          ethnicity ~ "categorical"),
              statistic = list(all_continuous() ~ "{mean} ({sd})",
                              all_categorical() ~ "{n} ({p}%)"),
              digits = list(everything() ~ c(2))) %>%
  as_gt()

demo_table

demo_table %>%
  gt::gtsave("Tables/demo_table.html")
